Semi-permeable vesicles: mathematical formulation, numerics and physics

### 2020-02-25 vesicle_code/docs/permeableVes/main.tex
small changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\subsection{Discretization in Space}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\subsection{Discretization in Space}
We apply a collocation method where the vesicle is discretized at $N$
points. We need to compute derivatives of functions defined on the
vesicle boundary, and these are done with Fourier differentiation.
Finally, to compute the single-layer potential, we use an eight-order
Alpert quadrature rule~\cite{alp1999} which resolves the logarithmic
singularity of the integrand.
